Functional requirements are categorised using the MoSCoW model.
The MoSCoW model consists of:
\begin{enumerate}
  \item Must-haves:\\
    Must-haves must be implemented during the alpha and must be finished
    before the beta starts.
  \item Should-haves:\\
    Should-haves must be implemented during the beta and must be finished
    before the product is released.
  \item Could-haves:\\
    Could-haves should be implemented during the beta if all should-haves are
    implemented. All other remaining could-haves should be implemented during
    incremental release cycles.
  \item Wont-haves:\\
    Wont-haves will not be implemented. They are stated to clearly describe
    what features the tool is not designed for.
\end{enumerate}

\subsubsection{Must-haves}

\begin{enumerate}
  \item The user must be able to log in using Single-log on

  \item Administrators must be able to appoint a user as teacher of a course

  \item A teacher must be able to create assignments for a course
    \begin{enumerate}
      \item An assignment must have an optional deadline

      \item An assignment must have a suggested length

      \item An assignment must have a name

      \item An assignment must have an optional description
    \end{enumerate}

  \item A user must be able to subscribe to a course, making him student for
    a course

  \item A student must be able to view a calendar
    \begin{enumerate}
      \item The calendar must have a week view (desktop-only)

      \item The calendar must have a month view (desktop-only)

      \item The calendar must have a day view
    \end{enumerate}

  \item A teacher must be able to view upcoming assignments in a course overview

  \item A teacher must be able to edit existing upcoming assignments

  \item A student must be able to view upcoming assignments next to the calendar.
    The calendar must only show assignments that fit the current selected
    time-frame. The assignments must be sorted by earliest deadline first.
    \begin{enumerate}
      \item An upcoming assingment must have the height corresponding to the
        pre-defined suggested length (desktop-only)

      \item An upcoming assignment must have a title with the name

      \item An upcoming assignment must have a sub-title with the deadline.
        If the assignment has no deadline, the time is shown the exam is
        scheduled for the course
    \end{enumerate}

  \item A student must not be able to edit assignments of other students

  \item A student must be able to view an upcoming assignment
    \begin{enumerate}
      \item The upcoming assignment must be placed in the center of the screen

      \item The upcoming assignment must show the description, if it exists

      \item The upcoming assignment must have a button to schedule the assignment.
        (See next point)
    \end{enumerate}

  \item A student must be able to schedule an upcoming assignment
    \begin{enumerate}
      \item A student must not be able to schedule an assignment in the past

      \item A student must be able to drag the assignment on the calendar

      \item A student must be able to save the scheduled assignment

      \item A student must be able to edit the scheduled time of an assignment
    \end{enumerate}

  \item A student must be able to finish an assignment
    \begin{enumerate}
      \item A student must not be able to finish assignments where the scheduled
        start time has not been yet

      \item A student must not be able to finish already finished assignments

      \item A student must be able to set an actual spent time
    \end{enumerate}

  \item A student must be able to view a list of assignments that he/she missed.
    Missed is defined as all planned assignments which have not been finished
    for more than 1 day, aswell as all unplanned passed assignments

\end{enumerate}

\subsubsection{Should-haves}

\subsubsection{Could-haves}
  \item The calendar will not be able to be exported to other calendars

\subsubsection{Wont-haves}

\begin{enumerate}
  \item The system will not be translated into languages other than English

  \item The system will not be usable without internet

  \item The system will not be usable without enabling Javascript

  \item The calendar will not be customizable
\end{enumerate}

\input{scenarios}

\input{endpoints}
